### 2023-08-08 application.tex
solved endproof
section

\end{proof}
%		l'état atteint $s'$ est au dessus des minimaux de $\pred^*(X)$, ainsi par (upward) compatibility on sera toujours capable d'aller dans $X$. 
%
%
%\noindent
%{\bf Vector addition system with states}
%

\section{Resilience for VASS}

@@

\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

This all changes when you add control states. For a VASS with control states in $Q$, a set $\Bad = \uparrow \Bad$, for all $q \in Q$, either there is an element of the basis of $\Bad$ with state $q$ \----
then $q(\textbf{v})$ with $\textbf{v} > \textbf{v}_{\Bad}$ is necessarily in $\Bad$ by upward closure; if this hold for all $q \in Q$, then $k$-resilience does not hold \---- either there is none. If there is none, then 
$\uparrow q(\textbf{0})$
 is in the complement of $\Bad$, i.e. $\Safe$. One can then exhibit upward-closed subsets of 
 $\Safe$ and compute basis for the sets of elements from which they are reachable in at most $k$ steps. 
Substracting these predecessor from $\Bad$ yields either a finite number of elements from which one has to check $\Safe$ is reachable in at most $k$ steps, either an infinite number of elements of which there is one which cannot reach $\Safe$ in at most $k$ steps \-- for much the same reasons {\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$. This lead to a decision procedure, written in detail in Appendix~\ref{appendix brp VASS}, which lead to the following decidability result:

>>>>

%		l'état atteint $s'$ est au dessus des minimaux de $\pred^*(X)$, ainsi par (upward) compatibility on sera toujours capable d'aller dans $X$. 
%
%
%\noindent
%{\bf Vector addition system with states}
%

\section{Resilience for VASS and variations}

@@

\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system \alain{pas défini}when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

This all changes when one considers VASS (having control states). For a VASS $V = (Q,T)$, a set $\Bad = \uparrow \Bad$, for all $q \in Q$, either there is an element of the basis of $\Bad$ with state $q$ \----
then $q(\textbf{v})$ with $\textbf{v} > \textbf{v}_{\Bad}$ is necessarily in $\Bad$ by upward closure; if this hold for all $q \in Q$, then $k$-resilience does not hold \---- either there is none. If there is none, then 
$\uparrow q(\textbf{0})$
 is in the complement of $\Bad$, i.e. $\Safe$. One can then exhibit upward-closed subsets of 
 $\Safe$ and compute basis for the sets of elements from which they are reachable in at most $k$ steps. 
Substracting these predecessor from $\Bad$ yields either a finite number of elements from which one has to check $\Safe$ is reachable in at most $k$ steps, either an infinite number of elements of which there is one which cannot reach $\Safe$ in at most $k$ steps \-- for much the same reasons {\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$. This lead to a decision procedure, written in detail in Appendix~\ref{appendix brp VASS}, which lead to the following decidability result:
